Crunching Large Graphs with Commodity Processors

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
modified:   softxmt-hotpar2011.tex
spelling

% Whereas in the PGAS model coherency of global copies is implictly
% maintained across the system, % \todo{cite pgas?}
% we completely forego
% caching of globally shared data.

@@

\item[Low overhead synchronization:] 
  We must support global synchronization between threads that allows unrelated threads to proceed unblocked.
\end{description}
We discuss our approach to solving each of these challenges in
turn. For each one, we discuss both our current single-node
implementation and ideas for a multi-node implementation.

@@

%\paragraph{Multi-node ideas.}
In a multi-node implementation, synchronization operations can be delegated to a memory manager
thread or accelerator. Sychronization on remote data would be
performed by the remote memory manager. This may simplify the
implementation: if only a single core (or single accelerator) is
accessing the data being synchronized, the use of memory fences may be
reduced or eliminated.

@@

Our evaulation consists of two parts. First, we demonstrate that the
runtime system can achieve the same performance as when 
explicit memory concurrency is available. Second, we look at the runtime
within the multi-node picture and show that it can tolerate large
latencies. In each part we begin by studying relevant aspects of our
test machine's memory system so we can interpret our runtime results.

>>>>

% Whereas in the PGAS model coherency of global copies is implicitly
% maintained across the system, % \todo{cite pgas?}
% we completely forego
% caching of globally shared data.

@@

\item[Low overhead synchronization:] 
%  We must support global synchronization between threads that allows unrelated threads to proceed unblocked.
  A thread that is synchronizing must yield its core to allow others to make progress.
\end{description}
We discuss our approach to solving each of these challenges in
turn. For each one, we discuss both our current single-node
implementation and ideas for a multi-node implementation.

@@

%\paragraph{Multi-node ideas.}
In a multi-node implementation, synchronization operations can be delegated to a memory manager
thread or accelerator. Synchronization on remote data would be
performed by the remote memory manager. This may simplify the
implementation: if only a single core (or single accelerator) is
accessing the data being synchronized, the use of memory fences may be
reduced or eliminated.

@@

Our evaluation consists of two parts. First, we demonstrate that the
runtime system can achieve the same performance as when 
explicit memory concurrency is available. Second, we look at the runtime
within the multi-node picture and show that it can tolerate large
latencies. In each part we begin by studying relevant aspects of our
test machine's memory system so we can interpret our runtime results.
